### 2015-07-29 simulation.Rmd
added hessian to output

The likelihood surface about the fitted and simulated values (red are the values simulated under, black is the fitted values):
```{r likelihood_surface, echo=FALSE, results="asis", fig.align='center'}
f <- function (x) { model@likfun((x*timevec)[model@results$use.par]) }
for (k in (1:nrow(mr_compare))[model@results$use.par]) {
    pvals <- seq( .9*min(mr_compare[k,c("fit","simulated")]), 1.1*max(mr_compare[k,c("fit","simulated")]), length.out=10 )
    inds <- 1:nrow(mr_compare)
    inds[k] <- 1+nrow(mr_compare)
    lvals <- sapply( pvals, function (x) { f( c(mr_compare$fit,x)[inds] ) } )
    l2vals <- sapply( pvals, function (x) { f( c(mr_compare$simulated,x)[inds] ) } )
    plot( pvals, lvals, type='b', main=paste("likelihood surface for", mr_compare$name[k]), ylab="log-likelihood", xlab='value', ylim=finite_range(lvals,l2vals) )
    lines( pvals, l2vals, col='red', type='b' )
    abline(v=mr_compare[k,c("fit","simulated")], col=c("black","red"))
}
```

>>>>

The profile likelihood surface about the fitted and simulated values (red are the values simulated under, black is the fitted values):
```{r likelihood_surface, echo=FALSE, results="asis", fig.align='center'}
f <- function (x) { model@likfun((x*timevec)[model@results$use.par]) }
for (k in (1:nrow(mr_compare))[model@results$use.par]) {
    pvals <- seq( .9*min(mr_compare[k,c("fit","simulated")]), 1.1*max(mr_compare[k,c("fit","simulated")]), length.out=10 )
    inds <- 1:nrow(mr_compare)
    inds[k] <- 1+nrow(mr_compare)
    lvals <- sapply( pvals, function (x) { f( c(mr_compare$fit,x)[inds] ) } )
    l2vals <- sapply( pvals, function (x) { f( c(mr_compare$simulated,x)[inds] ) } )
    plot( pvals, lvals, type='b', main=paste("likelihood surface for", mr_compare$name[k]), ylab="log-likelihood", xlab='value', ylim=finite_range(lvals,l2vals) )
    lines( pvals, l2vals, col='red', type='b' )
    abline(v=mr_compare[k,c("fit","simulated")], col=c("black","red"))
}
```

Here is the Hessian of the likelihood (obtained by numerical differentiation)
```{r likelihood_hessian, echo=FALSE}
# Hessian of the likelihood surface
likfun.hess <- hessian(function(x)fit.model@likfun(x*timevec[fit.model@results$use.par]),method.args=list(eps=min(coef(model)/10)),x=coef(model)[fit.model@results$use.par])
colnames( likfun.hess ) <- rownames( likfun.hess ) <- names(coef(fit.model))[fit.model@results$use.par]
pander(likfun.hess)
```
and its inverse (the asymptotic covariance matrix)
```{r likelihood_covariance, echo=FALSE}
# asymptotic covariance matrix
est.covmat <- ginv(likfun.hess)
pander(est.covmat)
```
and the corresponding correlation matrix
```{r likelihood_covariance, echo=FALSE}
# asymptotic covariance matrix
pander(cov2cor(est.covmat))
```
